Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex

\documentclass[11pt,twocolumn]{article} 
\usepackage[utf8]{inputenc}
\usepackage{simpleConference}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{url,hyperref}
\usepackage{tikz,pgfplots}

@@

When performing morphological analysis, there are a few different cases to consider: words that share similar
meaning but appear in diffrent syntactic contexts (``German"---``Germanic"), new words generated from
the combination of two separate words (``bookcase"|``book"---``case"), words with dissimilar meaning but
derived from one another ``insuffcient"---``sufficient"). In the first and last case, words are often related
by the addition of preffixes, suffixes, and other affixes. This allows us to form morphological chains - which
link a base word to its derivative through a series of affixations.
We wish to

@@

>>>>

\documentclass[11pt,twocolumn]{article} 
\usepackage[utf8]{inputenc}
\usepackage{simpleConference}
\usepackage[margin=1.125in]{geometry}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{times}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{url,hyperref}
\usepackage{tikz,pgfplots}

@@

When performing morphological analysis, there are a few different cases to consider: words that share similar
meaning but appear in different syntactic contexts (``German"---``Germanic"), new words generated from
the combination of two separate words (``bookcase"|``book"---``case"), words with dissimilar meaning but
derived from one another ``insufficient"---``sufficient"). In the first and last case, words are often related
by the addition of prefixes, suffixes, and other affixes. This allows us to form morphological chains - which
link a base word to its derivative through a series of affixations.

Most work in the field looks at either orthographic information or
semantic information. \citet{Narasimhan15} integrates these approaches by representing a word
with a series of derivations from the base form of the word, thereby capturing both types of information in each derivation.
At each step, the similarity across the derivation can be analyzed using both character similarity measures and semantic similarity measures.

@@

The Turkish language contains characters like \c{c} and \u{g} which are not in the English alphabet. In computing with them and in our results below, we have preprocessed the Turkish texts to replace characters not found in English with a capitalized letter. (We convert all words to lowercase beforehand, so there are no ambiguous symbols.)
